Reliable feature point matching without the use of geometric constraints

### 2013-06-06 text/clustering.tex
Fixed and compressed some introductory text

this idea by using the community structure in the similarity graph of 

@@

proposed in the literature to solve this problem. In particular many 
approaches look at the geometric configuration of the feature points and 
match them according to assumptions made about the geometric 
relationship between the images matched. These assumptions are then used 
to create constraints used to evaluate the matches such as angular 
constraints (\cite{kim2008efficient}), epipolar constraints 
(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}).

@@

Another approach proposed in the literature is to pick out different 
zones in each image and pair zones when correspondence pairs are mainly 
found going from one zone to another. This allows for the filtering of 
all correspondences that do not fall within paired zones.  
\cite{das2008event} proposes clustering feature points by using their 
geometric position and exclude correspondences that are geometrically 
deviant. A more sophisticated approach is introduced in 
\cite{wu2011robust} where the zones are created by using the MSER 
feature detector to find areas of interest in the images. These areas 
can be defined as an ellipse with a certain radius around the interest 
points. The feature points that fall within this ellipse are then 
matched according to epipolar constraints.  

@@

of the image to filter correspondences is not possible. This situation 
most often arise when the assumptions made by a geometric method aren't 
valid. In object recognition for example, adjecent objects in one photo 
might be separated in another. In addition methods using geometric 
constraints all require a set of correspondences to begin with. If this 
set of correspondences is narrowed down to a smaller set with a higher 
ratio of correct matches the result of the geometric matching will be 
both faster and more accurate.  Finally some use cases might require a 
performance that can't be achieved by a more complex geometric method 
where simple non geometric methods might be able to provide additional 
matching accuracy with a smaller performance penalty.
There are a relatively small number of algorithms proposed to solve the 
matching problem without involving geometric constraints. Traditionally 
the feature points of two images have been matched by comparing every 
feature point of one image with all feature points of the other and 
finding the best matches based on the similarity of the descriptors.  
With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
proposes an alternative measure where the uniqueness of a given match is 
found by looking at the two nearest neighbors of each feature point and 
calculating a match score by the ratio of similarities. By ranking the 
scores by their uniqueness and picking the $n$ best we get a set of 
correspondences that are distinctly matched across the two images.

@@

			\caption{Baseline Result}

@@

	\caption{Illustration of matches filtered by \emph{MM}}

@@

\emph{MM}. In figure \ref{fig:unique} the matches between two images are 
shown when using the \emph{SIFT} algorithm from \cite{lowe2004sift}. For 
each match found between the two images, a line has been drawn. The 
color of the line is green in case the match is correct and red for 
incorrect matches. Figure \ref{fig:within} shows the correspondences 
found by mirror match, but including all matches that are found within 
the same image. Notice how the by the bottom of the image admits 

@@

clustering the feature points displayed as a graph where each node 
correspond to a feature point. Here the border of nodes signifies the 
original image while the color of the node is decided by what partition 
it belongs to.  Notice that since a limited amount of colors are used 
disconnected subgraphs of the same color can be assumed to belong to 
separate partitions. Figure \ref{fig:cropped_graph} shows a detailed 
section of the graph where the interplay between small partitions 
consisting of two or three nodes as well as larger partitions consisting 
of several hundred nodes can be seen.

@@

	\caption{The partitioned feature graph. Every color signifies a 
	partition while the edge color of each node signifies which image it 
belongs to. Notice the many clusters with only two or three nodes.}

>>>>

this idea by using community structure in the similarity graph of 

@@

proposed in the literature to solve this problem. Many approaches look 
at the geometric configuration of the feature points and match them 
according to assumptions made about the geometric relationship between 
the images matched. These assumptions are then used to create 
constraints used to evaluate the matches such as angular constraints 
\cite{kim2008efficient}, epipolar constraints \cite{torr2000mlesac}, 
\cite{chum2005matching} and pairwise constraints \cite{choi2009robust}, 
\cite{leordeanu2005spectral}.

@@

Alternatively we can pick out different areas in each image and pair 
areas when correspondence pairs are mainly found going from one area to 
another. This allows for the filtering of all correspondences that do 
not fall within paired areas. Examples include \cite{das2008event} and 
\cite{wu2011robust}.
%proposes clustering feature points by using their geometric position 
%and exclude correspondences that are geometrically deviant. A more 
%sophisticated approach is introduced in \cite{wu2011robust} where the 
%areas are created by using the MSER feature detector to find areas of 
%interest in the images. These areas can be defined as an ellipse with a 
%certain radius around the interest points. The feature points that fall 
%within this ellipse are then matched according to epipolar constraints.  

@@

of the image to filter correspondences is not possible, such as object 
recognition where adjecent objects in one photo might be separated in 
another. Another example is images that do not overlap where algorithms 
might still find matches adhering to the imposed geometric constraints.
In addition methods using geometric constraints all require a set of 
correspondences to begin with. If this set of correspondences is 
narrowed down to a smaller set with a higher ratio of correct matches 
the result of the geometric matching will be both faster and more 
accurate.  Finally some use cases might require a performance that can't 
be achieved by a more complex geometric method where simple non 
geometric methods might be able to provide sufficient matching accuracy 
with a smaller performance penalty.

There are a relatively small number of algorithms proposed to solve the 
matching problem without involving geometric constraints. Traditionally 
the feature points of two images have been matched by comparing every 
feature point of one image with all feature points of the other and 
finding the best matches based on the similarity of the descriptors.  
With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
proposes an alternative measure where the uniqueness of a given match is 
found by looking at the two nearest neighbors of each feature point and 
calculating a match score by the ratio of similarities. By ranking the 
scores by their uniqueness and picking the $n$ best we get a set of 
correspondences that are distinctly matched across the two images. This 
method will be referred to as \emph{SIFT} in this paper.

@@

			\caption{SIFT}

@@

	\caption{Illustration of matches filtered by \emph{MM}. For each 
	correct match found between the two images, a green line is shown.  
Incorrect matches are marked with a red line. Figure \ref{fig:within} 
shows the correspondences found by mirror match, but including all 
matches that are found within the same image. }

@@

\emph{MM}. Notice how the by the bottom of the image admits 

@@

clustering the feature points displayed as a graph.

@@

	\caption{The partitioned feature graph. Each vertex represents a 
		feature point while an edge represent a high similarity between 
		points. A partition is a connected group marked by a color.  Due 
		to a limited amount of colors some disconnected partitions have 
		been assigned the same color. The edge color of each node 
		signifies which image it belongs to. In the detailed crop to the 
		right the various cluster sizes can be seen, ranging from 
	hundreds of feature points to only two or three.}
